\documentclass[a4paper, twoside, russian, ngerman]{book}%[a4paper,oneside] ngerman für "=
\usepackage[pass]{geometry}%[hmarginratio=1:1]{geometry}
\usepackage{makeidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathabx}
\usepackage{csquotes}
\usepackage{afterpage}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,backgrounds,arrows,calc,positioning}
\usetikzlibrary{calendar,fpu}

\usepackage{ifthen}
\usepackage{intcalc}

\usepackage[citecolor=black,urlcolor=black,linkcolor=black,breaklinks=true]{hyperref}
\hypersetup{
    colorlinks=true
}

% \usepackage[xindy={language=english}, % ,codepage=duden-utf8
%     nonumberlist,
%     toc,
%     nopostdot,
%     style=altlist,
%     nogroupskip
%     ]{glossaries}
%     %\GlsSetXdyCodePage{duden-utf8}
% \apptocmd{\thebibliography}{\raggedright}{}{}


\usepackage{fontspec}
\setromanfont{CMU Serif}
\setsansfont{CMU Sans Serif}
\setmonofont{CMU Typewriter Text}

%\makeatletter
%\renewcommand{\l@section}{\@dottedtocline{1}{1.5em}{2.6em}}
%\renewcommand{\l@subsection}{\@dottedtocline{2}{4.0em}{3.6em}}
%\renewcommand{\l@subsubsection}{\@dottedtocline{3}{7.4em}{4.5em}}
%\makeatother

%\setcounter{tocdepth}{2}
%\setcounter{secnumdepth}{0}

%\makeindex
%\makeglossaries


\begin{titlepage}
\centering
\title{Daggerheart Playtest}

\centering
\author{whoami}
\end{titlepage}

\begin{document}

\maketitle

\tableofcontents

\setlength{\parskip}{1ex}

\chapter{Who am I?}

So Othedias betrays the Gods, and they abbandon us all? How is that fair? They do not leave us, let us deal with the land. They shatter the God-King's domain, I suppose to punish him. Where does that leave us? How dare the Gods, God-King or original Gods!

And so it is up to us to figure out how to break out or restore this forsaken place. Well, that is what grand-grand-grand-father Ἐρατοσθένης believed. I am not so sure. Maybe it is just about being forskaen and withering away -- a people punished for their master and king. A king, Gods be damned, by birth, my people having had no say in it. Neither in what he did. A king, a God-King, absolute regent, total power, better no questions asked. Bow and pray. Maybe that was the problem, the Gods being envious they could no longer be prayed to. A plague on all their temples!


\chapter{Table Fitness}

The setting (frame) is dark, and the character is depressed. There certainly are risks with playing dark characters. It is important that the character is not isolating themselves. It is not improving much, relative to the table failure of making an unapproachable character, if one needs to explain lack of social engagement within the group by monologing their struggle. At least have strong Connections.


\end{document}
